\section{Introduction}
The development and research of compressed sensing applied to a single pixel camera (SPC) is a relative new area in signal processing with the first functioning camera architecture in 2006. Since then numerous improvements and methods have been proposed how to capture images. In this section a introduction to the SPC architecture and the theory of compressed sensing is presented followed by the aim, research questions and thesis outline of this master's thesis. 

\subsection{Single pixel camera architecture}


\subsection{Compressive sensing}
Compressive sensing is a relative new sampling strategy which reconstructs a compressible or spares signal by finding solution to undetermined linear system. The signal is encoded by a number of measurements using measurement matrices and can then be reconstructed from that encoded signal. Two constraints need to be fulfilled to apply compressed sensing sampling: the sampled signal needs to be spares in some basis e.g. Fourier, or gradient, the second condition is that the measurement matrix must be incoherent with the sparse transform.\\[0.1in]

The CS sampling model is defined as

\begin{equation}
\label{eq:CS1}
   \mathbf{ y = \Phi x + \epsilon}\text{,}
\end{equation}\\[0.1in]

where, $\mathbf{x}_{N\times1}$ is the signal with $N$ samples, $\mathbf{y}_{M\times1}$ is the vector with $M$ measurements, $\mathbf{\Phi}_{M \times N}$ is the measurements matrix (each unique sensing matrix as a column vector $1 \times N$) and $\mathbf{\epsilon}$ is the noise. In conventional sampling the number of measurements $M$ needs to be at least equal to the number of samples $N$ to recover the signal but CS states that $M$ can be relatively small compared to $N$ given how compressible the signal is. The signal $\mathbf{x}$ can be represented as  

\begin{equation}
\label{eq:CS2}
   \mathbf{ \Psi \theta = x }\text{,}
\end{equation}\\[0.1in]

where, $\mathbf{\Psi}_{N \times N}$ is some  basis matrix and
$\mathbf{\theta}_{N\times1}$ is the coefficients where $\mathbf{\theta}$ is $K$-sparse. $K$-sparse means that the signal $\mathbf{x}$ has $K$ non zero elements in basis $\mathbf{\Psi}$, $||\mathbf{\theta}||_0 = K$. Given equation~\ref{eq:CS2}, equation~\ref{eq:CS1} can be expand to


\begin{equation}
   \mathbf{ y = \Phi x + \epsilon = \Phi \Psi \theta + \epsilon = A \theta + \epsilon }\text{,}
\end{equation}\\[0.1in]

where, $A_{M \times N} = \Phi \Psi$ is the reconstruction matrix. The last statement is what makes CS powerful, a signal which is not sparse can be sampled with measurement matrix $\Phi$ and the reconstructed with reconstruction matrix $A$ in a basis where $x$ is sparse.

\subsection{Measurement matrix}
\subsubsection{Random}

\subsubsection{Walsh Hadamard}


\subsection{Reconstruction methods}

\subsubsection{$\ell_1$ minimization}

\subsubsection{Greedy algorithms}

\subsubsection{Total variation}


\subsection{Aim} 
What image quality can be achieved in natural images captured with a single pixel camera in daylight using state of the art methods?  


\subsection{Research questions} 
\label{sec:RQ}
\begin{itemize}
    \item How can the quality of images reconstructed by CS or a SPC be evaluated?
    \item What is the state of the art method to capture and reconstruct images using a SPC architecture?
    \item What image quality is achieved using state of the art methods applied to the SPC?
\end{itemize}


\subsection{Limitations}
\begin{itemize}
    \item The hardware rig provided by FOI
    \item 
\end{itemize}



\subsection{Thesis outline}
